---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{what the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup}
library(MATH4753ESSA24)
```

# Introduction

Here is the introduction of my package. I have the four functions from Lab4-8 for display per the requirements.  

## myread
The function from Lab4 which reads a csv into a variable. 
```{r}
seed <-MATH4753ESSA24::myread("SEEDLING.csv","C:/Users/coleh/OneDrive/Desktop/MATH4753/Lab/Lab4/")
head(seed)
```

## myf
The myf function from Lab 5 which shows binomial simulation. 
```{r}
MATH4753ESSA24::myf(iter = 10000, n= 10, p = 0.5)
```


## myncurve
The myncurve function from Lab 6 which shows continuous normal density
```{r}
MATH4753ESSA24::myncurve(10, 5, 6)
```

## myclt
MyCLT was used in Lab 8 to show the Central Limit Theorem. 
```{r fid.width = 50}
MATH4753ESSA24::myclt(n = 10, iter = 1000, a = 0, b = 5)
```


## Data
The data that was required to be upload into the package for Lab 7.
```{r}
library(MATH4753ESSA24)
knitr::kable(head(fire))
